Synthesis of Rules for Network Intrusion Detection

### 2019-10-19 paper/paper.tex
pass on abstract

\begin{document}
%
\title{Synthesis of Network Intrusion Detection Rules}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\inst{1}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\inst{1}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\inst{1}\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
...
\keywords{NIDS, synthesis, search}
\end{abstract}
%
%
%
\section{Introduction}

>>>>

\begin{document}
%
\title{Synthesis of Rules for Network Intrusion Detection}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Lucas Alcantara\inst{1}\Comment{\orcidID{0000-1111-2222-3333}} \and
Guilherme Padilha\inst{1}\Comment{\orcidID{1111-2222-3333-4444}} \and
Marcelo d'Amorim\inst{1}\Comment{\orcidID{0000-0002-1323-8769}}}
%
\authorrunning{Alcantara et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Federal University of Pernambuco (UFPE), Recife, Brazil\\
\email{\{lama,ghps,damorim\}@cin.ufpe.br}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the network
traffic against a pre-defined set of rules, which can become obsolete
as attackers learn new strategies to circumvent existing defenses.
This paper proposes \tname{}, a technique that automatically
synthesizes \nids\ rules from positive and negative examples (\ie{},
malicious and benign traffic). \tname{} formulates synthesis as an
optimization problem whose candidate solutions are rules that
maximizes the captured the positive traffic and minimizes the captured
negative traffic. \tname{} bootstraps the search with candidate
solutions that use data from the payload of the malicious message and
produces optimal rule candidates on output. We evaluated \tname{} on a
diverse set of attacks. Results indicate that \Fix{...}

%% optimizes the
%% candidate solution to capture the positive example and, and then
%% optimizes the candidate solution to avoid capturing the negative
%% traffic.

\keywords{NIDS, synthesis, search}
\end{abstract}
%
%
%
\section{Introduction}
